### 2021-05-10 manuscript.Rmd
Add qPCR posterior contrast.

---
#title: "Healthcare Micro-Environments Define Multidrug-Resistant Organism Persistence"  
#author: "Brendan J. Kelly, MD, MS"  
bibliography: bib/references.bib
csl: csl/journal-of-clinical-microbiology.csl
output: html_document
css: style_helvetica_double.css
---

>>>>

---
#title: "Healthcare Micro-Environments Define Multidrug-Resistant Organism Persistence"  
#author: "Brendan J. Kelly, MD, MS"  
bibliography: bib/references.bib
csl: csl/infection-control-and-hospital-epidemiology.csl
output: html_document
css: style_helvetica_double.css
---
